\ac{THOR} currently includes four tutorials to guide new users through the process of creating a mesh with Gmsh, using OpenMeshConverter to make it a \ac{THOR} mesh, and running \ac{THOR} using that mesh.
The first tutorial is the Godiva tutorial, creating a model of the bare Godiva critical experiment sphere, meshing it, and running it with \ac{THOR}.
This tutorial demonstrates basic \ac{THOR} problem creation and running concepts.

The second tutorial is the BeRP tutorial, creating a model of the BeRP ball with 3 inches of polyethylene reflector surrounding the BeRP ball.
This tutorial demonstrates a more advanced problem involving multiple materials and regions.
Additionally, this is a fixed source problem used to demonstrate the fixed source capabilities of the THOR transport solver.

Since the first two systems are physically equivalent to one-dimensional spherical problems, the symmetry is taken advantage of and the problems are modeled using a one/eighth model with reflective boundary conditions to be equivalent to the full spheres for the tutorial.
In the tutorial folders, \\
\verb"<thor_dir>/THOR/examples/tutorials/Godiva" and \verb"<thor_dir>/THOR/examples/tutorials/BeRP", versions of these tutorials with full spheres, half spheres, and quarter spheres are also included along with reference results.

The third tutorial involved the BeRP sphere again, this time with the SNAP detector right beside it.
This demonstrates a much more advanced meshing problem with variable fields of mesh size factors to mesh the smaller regions finer for better resolution.
Additionally, this fixed source problem demonstrates the usage of the THOR detector response calculator post-processor.

The fourth tutorial features an infinite 3D lattice eigenvalue problem using the BEAVRS fuel pincell.
This tutorial features extruded meshes, though the THOR portion of this calculation is relatively simple.

Note that these tutorials all rely on pre-processors included as THOR submodules in \verb"<thor_dir>/pre-processors" and some rely on post-processors included as THOR submodules in \verb"<thor_dir>/post-processors".
So the user should make sure to compile those tools before attempting these tutorials.

\section{Godiva Tutorial}

\input{chapters/tutorials/godiva.tex}

\section{Polyethylene Shielded BeRP Ball Tutorial}

\input{chapters/tutorials/berp.tex}

\section{Bare BeRP Ball With SNAP Detector Tutorial}

\input{chapters/tutorials/snap-berp.tex}
